---
title: "results-temp"
author: "Gloria Kang"
output:
  html_notebook: 
    code_folding: hide
    theme: cosmo
  pdf_document: default
  html_document: 
    keep_md: yes
    self_contained: no
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
rm(list = ls(all.names = TRUE))
```

```{r}
# load RData
load("output/vaxbase_10.RData")
#load("output/vaxbase_20.RData")
#load("output/vaxbase_30.RData")
#load("output/vaxbase_40.RData")
#load("output/vaxbase_50.RData")
#load("output/vaxbase_60.RData")

#load("output/vax70_10.RData")
#load("output/vax70_20.RData")
#load("output/vax70_30.RData")
#load("output/vax70_40.RData")
#load("output/vax70_50.RData")
#load("output/vax70_60.RData")
```

# Clinical costs (high, low, all)
```{r}
costs_04_high; costs_04_low; costs_04_high + costs_04_low
costs_519_high; costs_519_low; costs_519_high + costs_519_low
costs_2064_high; costs_2064_low; costs_2064_high + costs_2064_low
costs_65_high; costs_65_low; costs_65_high + costs_65_low
```

# Number of cases (high, low, all)
```{r}
cases_04_high; cases_04_low; cases_04_high + cases_04_low
cases_519_high; cases_519_low; cases_519_high + cases_519_low
cases_2064_high; cases_2064_low; cases_2064_high + cases_2064_low
cases_65_high; cases_65_low; cases_65_high + cases_65_low
```

# Cost difference (high, low, all)
```{r}
icer_04_high[1]; icer_04_low[1]; (cost_diff_04 <- icer_04_high[1] + icer_04_low[1])
icer_519_high[1]; icer_519_low[1]; (cost_diff_519 <- icer_519_high[1] + icer_519_low[1])
icer_2064_high[1]; icer_2064_low[1]; (cost_diff_2064 <- icer_2064_high[1] + icer_2064_low[1])
icer_65_high[1]; icer_65_low[1]; (cost_diff_65 <- icer_65_high[1] + icer_65_low[1])
```

## Total cost difference in scenario
```{r}
(total_cost_difference <- cost_diff_04 + cost_diff_519 + cost_diff_2064 + cost_diff_65)
```

# Cases averted (high, low, all)
```{r}
icer_04_high[2]; icer_04_low[2]; (case_avert_04 <- icer_04_high[2] + icer_04_low[2])
icer_519_high[2]; icer_519_low[2]; (case_avert_519 <- icer_519_high[2] + icer_519_low[2])
icer_2064_high[2]; icer_2064_low[2]; (case_avert_2064 <- icer_2064_high[2] + icer_2064_low[2])
icer_65_high[2]; icer_65_low[2]; (case_avert_65 <- icer_65_high[2] + icer_65_low[2])
```
## Total cases averted in scenario
```{r}
(total_cases_averted <- case_avert_04 + case_avert_519 + case_avert_2064 + case_avert_65)
```

# ICER per case averted (high, low, all)
```{r}
icer_04_high[3]; icer_04_low[3]; (icer_04_high[1] + icer_04_low[1]) / (icer_04_high[2] + icer_04_low[2])
icer_519_high[3]; icer_519_low[3]; (icer_519_high[1] + icer_519_low[1]) / (icer_519_high[2] + icer_519_low[2])
icer_2064_high[3]; icer_2064_low[3]; (icer_2064_high[1] + icer_2064_low[1]) / (icer_2064_high[2] + icer_2064_low[2])
icer_65_high[3]; icer_65_low[3]; (icer_65_high[1] + icer_65_low[1]) / (icer_65_high[2] + icer_65_low[2])
```
## Total ICER per case averted in scenario
```{r}
total_cost_difference / total_cases_averted
```

# Deaths (high, low, all)
```{r}
deaths_04_high[3]; deaths_04_low[3]; deaths_04_high[3] + deaths_04_low[3]
deaths_519_high[3]; deaths_519_low[3]; deaths_519_high[3] + deaths_519_low[3]
deaths_2064_high[3]; deaths_2064_low[3]; deaths_2064_high[3] + deaths_2064_low[3]
deaths_65_high[3]; deaths_65_low[3]; deaths_65_high[3] + deaths_65_low[3]
```

# Deaths averted (high, low, all)
```{r}
deaths_04_high[1]; deaths_04_low[1]; (death_avert_04 <- deaths_04_high[1] + deaths_04_low[1])
deaths_519_high[1]; deaths_519_low[1]; (death_avert_519 <- deaths_519_high[1] + deaths_519_low[1])
deaths_2064_high[1]; deaths_2064_low[1]; (death_avert_2064 <- deaths_2064_high[1] + deaths_2064_low[1])
deaths_65_high[1]; deaths_65_low[1]; (death_avert_65 <- deaths_65_high[1] + deaths_65_low[1])
```

## Total deaths averted in scenario
```{r}
(total_deaths_averted <- death_avert_04 + death_avert_519 + death_avert_2064 + death_avert_65)
```

# ICER per death averted (high, low, all)
```{r}
deaths_04_high[2]; deaths_04_low[2]; (icer_04_high[1] + icer_04_low[1]) / (deaths_04_high[1] + deaths_04_low[1])
deaths_519_high[2]; deaths_519_low[2]; (icer_519_high[1] + icer_519_low[1]) / (deaths_519_high[1] + deaths_519_low[1])
deaths_2064_high[2]; deaths_2064_low[2]; (icer_2064_high[1] + icer_2064_low[1]) / (deaths_2064_high[1] + deaths_2064_low[1])
deaths_65_high[2]; deaths_65_low[2]; (icer_65_high[1] + icer_65_low[1]) / (deaths_65_high[1] + deaths_65_low[1])
```

## Total ICER per death averted in scenario
```{r}
total_cost_difference / total_deaths_averted
```

# Other health outcomes
```{r}
outcomes_04_high; outcomes_04_low
outcomes_519_high; outcomes_519_low
outcomes_2064_high; outcomes_2064_low
outcomes_65_high; outcomes_65_low
```


