---
title: "Prevalent vax vs. No vax (40% VE)"
output: 
  html_notebook: 
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    theme: cosmo
    toc: yes
  html_document: 
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    theme: cosmo
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	warning = TRUE,
	cache = TRUE,
	tidy = TRUE
)
```

```{r}
rm(list = ls(all.names = TRUE))

library(ggplot2)
library(tidyr)
library(dplyr)
library(knitr)
library(rmarkdown)
library(formatR)
```

```{r}
data <- read.csv("df/icer-all.csv", as.is = TRUE)

# subset comparator = base
df <- data[(data$scenario=="vaxbase"),]

df$cost.diff.per100k <- as.numeric(df$cost.diff.per100k)
df$cases.averted <- as.numeric(df$cases.averted)
df$cases.averted.per100k <- as.numeric(df$cases.averted.per100k)
df$icer.case.averted <- as.numeric(df$icer.case.averted)
df$deaths.averted <- as.numeric(df$deaths.averted)
df$deaths.averted.per100k <- as.numeric(df$ deaths.averted.per100k)
df$icer.death.averted <- as.numeric(df$icer.death.averted)
df$dalys <- as.numeric(df$dalys)
df$dalys.per100k <- as.numeric(df$dalys.per100k)
df$dalys.averted <- as.numeric(df$dalys.averted)
df$dalys.averted.per100k <- as.numeric(df$dalys.averted.per100k)
df$icer.daly.averted <- as.numeric(df$icer.daly.averted)
```

```{r}
# subset efficacy
df <- df[!(df$scenario == 'vaxbase' & df$v.eff %in% c(50, 60)),]

# factors
df$age <- factor(df$age, levels = c("0-4 yrs", "5-19 yrs", "20-64 yrs", "65+ yrs", "All"))
df$risk <- factor(df$risk, levels = c("High", "Non-high", "All"))
df$scenario <- factor(df$scenario, levels = c("vaxbase", "vax70"))
df$v.eff <- factor(df$v.eff)
```

# Tables

```{r eval=FALSE, include=FALSE}
## Table: ICERs.
t1 <- df[c("scenario", "age", "risk", "v.eff", "icer.case.averted", "icer.death.averted", "icer.daly.averted")] %>%
  gather("icer.case.averted", "icer.death.averted", "icer.daly.averted", key = "icer", value = "value") %>%
  spread(risk, value) %>%
  arrange(scenario, v.eff, icer)
head(t1)
#write.csv(t1, "df/df2-icer.csv")

## Table: Cases, deaths, DALYs per 100,000 population.
t2 <- df[c("scenario", "age", "risk", "v.eff", "cases.per100k", "deaths.per100k", "dalys.per100k")] %>%
  gather("cases.per100k", "deaths.per100k", "dalys.per100k", key = "metric", value = "value") %>%
  spread(risk, value) %>%
  arrange(scenario, v.eff, metric)
head(t2)
#write.csv(t2, "df/df2-rates.csv")

## Table: Cases, deaths, DALYs averted per 100,000
t3 <- df[c("scenario", "age", "risk", "v.eff", "cases.averted.per100k", "deaths.averted.per100k", "dalys.averted.per100k")] %>%
  gather("cases.averted.per100k", "deaths.averted.per100k", "dalys.averted.per100k", key = "metric", value = "value") %>%
  spread(risk, value) %>%
  arrange(scenario, v.eff, metric)
head(t3)
#write.csv(t3, "df/df2-averted-rates.csv")
```

# Subset data.

```{r}
# subset scenario
df_base <- df[(df$scenario == 'vaxbase'),]

# age groups
age_df_base <- df_base[(df_base$risk == "All"),]

# risk groups
risk_df_base <- df_base[!(df_base$age == 'All'),]
```

## 40% VE: ICER per case averted
```{r}
ggplot(df_base[(df_base$v.eff == "40"),], aes(x = age, y = icer.case.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + 
  ylab("$ saved per case averted") + ggtitle("Prevalent Vaccination (40% efficacy): ICER per case averted")
```

## 40% VE: ICER per death averted
```{r}
ggplot(df_base[(df_base$v.eff == "40"),], aes(x = age, y = icer.death.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + 
  ylab("$ saved per death averted") + ggtitle("Prevalent Vaccination (40% efficacy): ICER per death averted")
```

## 40% VE: ICER per DALY averted
```{r}
ggplot(df_base[(df_base$v.eff == "40"),], aes(x = age, y = icer.daly.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + 
  ylab("$ saved per DALY averted") + ggtitle("Prevalent Vaccination (40% efficacy): ICER per DALY averted")
```


## 40% VE: Cases, cases averted
```{r}
g4 <- ggplot(df_base[(df_base$v.eff == "40"),], aes(x = age, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group")

g4 + aes(y = cases) + labs(y = "Cases", title = "Prevalent Vaccination (40% VE): Cases")
g4 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "Prevalent Vaccination (40% VE): Cases per 100k")
g4 + aes(y = cases.averted) + labs(y = "Cases averted", title = "Prevalent Vaccination (40% VE): Cases averted")
g4 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "Prevalent Vaccination (40% VE): Cases averted per 100k")
```

## 40% VE: Deaths, deaths averted
```{r}
g4 + aes(y = deaths) + labs(y = "Deaths", title = "Prevalent Vaccination (40% VE): Deaths")
g4 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "Prevalent Vaccination (40% VE): Deaths per 100k")
g4 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "Prevalent Vaccination (40% VE): Deaths averted")
g4 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "Prevalent Vaccination (40% VE): Deaths averted per 100k")
```

## 40% VE: DALYs, DALYs averted
```{r}
g4 + aes(y = dalys) + labs(y = "DALYs", title = "Prevalent Vaccination (40% VE): DALYs")
g4 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "Prevalent Vaccination (40% VE): DALYs per 100k")
g4 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "Prevalent Vaccination (40% VE): DALYs averted")
g4 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "Prevalent Vaccination (40% VE): DALYs averted per 100k")
```

## Fig. Cost-effectiveness plane (40% VE)

```{r}
g5 <- ggplot(df_base, aes(x = dalys.averted.per100k, y = cost.diff.per100k)) +
  labs(x = "DALYs averted per 100K", y = "Cost saved per 100K", title = "Prevalent Vaccination: Cost saved vs. DALYs averted")

g5 + aes(color = risk, group = risk) + geom_point() + facet_grid(v.eff ~ age)

g5 + aes(color = age, group = age) + geom_point() + facet_grid(v.eff ~ risk)
```


# Prevalent vax vs. No vax (All VE)
## Fig. ICER per case averted

```{r}
t <- labs(y = "$ saved per case averted", title = "Prevalent Vaccination: ICER per case averted")

ggplot(age_df_base, aes(x = age, y = icer.case.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy") + t

ggplot(df_base[(df_base$age=="All"),], aes(x = v.eff, y = icer.case.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy (%)", color = "Risk") + t

ggplot(df_base, aes(x = age, y = icer.case.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + t +
  facet_grid(~ v.eff)
```

## Fig. ICER per death averted

```{r}
t <- labs(y = "$ saved per death averted", title = "Prevalent Vaccination: ICER per death averted")

ggplot(age_df_base, aes(x = age, y = icer.death.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy") + t

ggplot(df_base[(df_base$age=="All"),], aes(x = v.eff, y = icer.death.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy (%)", color = "Risk") + t

ggplot(df_base, aes(x = age, y = icer.death.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + t +
  facet_grid(~ v.eff)
```

## Fig. ICER per DALY averted

```{r}
t <- labs(y = "$ saved per DALY averted", title = "Prevalent Vaccination: ICER per DALY averted")

ggplot(age_df_base, aes(x = age, y = icer.daly.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy") + t

ggplot(df_base[(df_base$age=="All"),], aes(x = v.eff, y = icer.daly.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy (%)", color = "Risk") + t

ggplot(df_base, aes(x = age, y = icer.daly.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + t +
  facet_grid(~ v.eff)
```


## Set up plots.

```{r}
# age
g1 <- ggplot(age_df_base, aes(x = age, group = v.eff, color = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy")
# risk
g2 <- ggplot(df_base[(df_base$age=="All"),], aes(x = v.eff, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy", color = "Risk group")

g3 <- ggplot(risk_df_base, aes(x = age, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") +
  facet_grid(~ v.eff)
```

## Fig. Cases, cases averted

```{r}
# age groups
g1 + aes(y = cases) + labs(y = "Cases", title = "Prevalent Vaccination: Cases")
g1 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "Prevalent Vaccination: Cases per 100k")
g1 + aes(y = cases.averted) + labs(y = "Cases averted", title = "Prevalent Vaccination: Cases averted")
g1 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "Prevalent Vaccination: Cases averted per 100k")

# risk groups
g2 + aes(y = cases) + labs(y = "Cases", title = "Prevalent Vaccination: Cases")
g2 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "Prevalent Vaccination: Cases per 100k")
g2 + aes(y = cases.averted) + labs(y = "Cases averted", title = "Prevalent Vaccination: Cases averted")
g2 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "Prevalent Vaccination: Cases averted per 100k")

g3 + aes(y = cases) + labs(y = "Cases", title = "Prevalent Vaccination: Cases")
g3 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "Prevalent Vaccination: Cases per 100k")
g3 + aes(y = cases.averted) + labs(y = "Cases averted", title = "Prevalent Vaccination: Cases averted")
g3 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "Prevalent Vaccination: Cases averted per 100k")
```

## Fig. Deaths, deaths averted

```{r}
# age groups
g1 + aes(y = deaths) + labs(y = "Deaths", title = "Prevalent Vaccination: Deaths")
g1 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "Prevalent Vaccination: Deaths per 100k")
g1 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "Prevalent Vaccination: Deaths averted")
g1 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "Prevalent Vaccination: Deaths averted per 100k")

# risk groups
g2 + aes(y = deaths) + labs(y = "Deaths", title = "Prevalent Vaccination: Deaths")
g2 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "Prevalent Vaccination: Deaths per 100k")
g2 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "Prevalent Vaccination: Deaths averted")
g2 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "Prevalent Vaccination: Deaths averted per 100k")

g3 + aes(y = deaths) + labs(y = "Deaths", title = "Prevalent Vaccination: Deaths")
g3 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "Prevalent Vaccination: Deaths per 100k")
g3 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "Prevalent Vaccination: Deaths averted")
g3 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "Prevalent Vaccination: Deaths averted per 100k")
```

## Fig. DALYs, DALYs averted

```{r}
# age groups
g1 + aes(y = dalys) + labs(y = "DALYs", title = "Prevalent Vaccination: DALYs")
g1 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "Prevalent Vaccination: DALYs per 100k")
g1 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "Prevalent Vaccination: DALYs averted")
g1 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "Prevalent Vaccination: DALYs averted per 100k")
# risk groups
g2 + aes(y = dalys) + labs(y = "DALYs", title = "Prevalent Vaccination: DALYs")
g2 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "Prevalent Vaccination: DALYs per 100k")
g2 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "Prevalent Vaccination: DALYs averted")
g2 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "Prevalent Vaccination: DALYs averted per 100k")

g3 + aes(y = dalys) + labs(y = "DALYs", title = "Prevalent Vaccination: DALYs")
g3 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "Prevalent Vaccination: DALYs per 100k")
g3 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "Prevalent Vaccination: DALYs averted")
g3 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "Prevalent Vaccination: DALYs averted per 100k")
```

## Fig. Cost-effectiveness plane (All VE)

```{r}
l <- labs(x = "DALYs averted per 100K", y = "Cost per 100K")

# All VE%
a <- ggplot(df_base, aes(x = dalys.averted.per100k, y = cost.diff.per100k)) + l +
  labs(title = "Cost-effectiveness plane: Prevalent Vaccination vs. No Vaccination")

a + aes(color = risk, group = risk) + labs(color = "Risk") + geom_point() + facet_grid(v.eff ~ age)
a + aes(color = age, group = age) + labs(color = "Age group") + geom_point() + facet_grid(v.eff ~ risk)
```
