---
title: "figures"
output: 
  html_notebook: 
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    theme: cosmo
    toc: yes
  html_document: 
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    theme: cosmo
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = TRUE,
	cache = TRUE,
	tidy = TRUE
)
```

```{r}
rm(list = ls(all.names = TRUE))

library(ggplot2)
library(tidyr)
library(dplyr)
library(knitr)
library(rmarkdown)
library(formatR)
```

```{r}
data <- read.csv("df/icer-all.csv", as.is = TRUE)
df <- data[(data$reference=="base"),]

df$cost.diff.per100k <- as.numeric(df$cost.diff.per100k)
df$cases.averted <- as.numeric(df$cases.averted)
df$cases.averted.per100k <- as.numeric(df$cases.averted.per100k)
df$icer.case.averted <- as.numeric(df$icer.case.averted)
df$deaths.averted <- as.numeric(df$deaths.averted)
df$deaths.averted.per100k <- as.numeric(df$ deaths.averted.per100k)
df$icer.death.averted <- as.numeric(df$icer.death.averted)
df$dalys <- as.numeric(df$dalys)
df$dalys.per100k <- as.numeric(df$dalys.per100k)
df$dalys.averted <- as.numeric(df$dalys.averted)
df$dalys.averted.per100k <- as.numeric(df$dalys.averted.per100k)
df$icer.daly.averted <- as.numeric(df$icer.daly.averted)
```

```{r}
# subset relevant efficacies
df2 <- df[!(df$scenario == 'vaxbase' & df$v.eff %in% c(50, 60)),]
#table(df2$v.eff, useNA = 'always')

df3 <- df2[!(df2$scenario == 'vax70' & df2$v.eff %in% c(30,40)), ]
#table(df3$scenario, df3$v.eff, useNA = 'always')

# factors
df3$age <- factor(df3$age, levels = c("0-4 yrs", "5-19 yrs", "20-64 yrs", "65+ yrs", "All"))
df3$risk <- factor(df3$risk, levels = c("High", "Non-high", "All"))
df3$scenario <- factor(df3$scenario, levels = c("vaxbase", "vax70"))
df3$v.eff <- factor(df3$v.eff)
```

# Tables

```{r eval=FALSE, include=FALSE, echo=TRUE}
## Table: ICERs.
t1 <- df3[c("scenario", "age", "risk", "v.eff", "icer.case.averted", "icer.death.averted", "icer.daly.averted")] %>%
  gather("icer.case.averted", "icer.death.averted", "icer.daly.averted", key = "icer", value = "value") %>%
  spread(risk, value) %>%
  arrange(scenario, v.eff, icer)
head(t1)
#write.csv(t1, "table-icer.csv")

## Table: Cases, deaths, DALYs per 100,000 population.
t2 <- df3[c("scenario", "age", "risk", "v.eff", "cases.per100k", "deaths.per100k", "dalys.per100k")] %>%
  gather("cases.per100k", "deaths.per100k", "dalys.per100k", key = "metric", value = "value") %>%
  spread(risk, value) %>%
  arrange(scenario, v.eff, metric)
head(t2)
#write.csv(t2, "table-rates.csv")

## Table: Cases, deaths, DALYs averted per 100,000
t3 <- df3[c("scenario", "age", "risk", "v.eff", "cases.averted.per100k", "deaths.averted.per100k", "dalys.averted.per100k")] %>%
  gather("cases.averted.per100k", "deaths.averted.per100k", "dalys.averted.per100k", key = "metric", value = "value") %>%
  spread(risk, value) %>%
  arrange(scenario, v.eff, metric)
head(t3)
#write.csv(t3, "table-averted-rates.csv")
```

# Subset data.
```{r}
# subset scenario
df_base <- df3[(df3$scenario == 'vaxbase'),]
df_vax70 <- df3[(df3$scenario == 'vax70'),]

# age groups
age_df_base <- df_base[(df_base$risk == "All"),]
age_df_vax70 <- df_vax70[(df_vax70$risk == "All"),]

# risk groups
risk_df_base <- df_base[!(df_base$age == 'All'),]
risk_df_vax70 <- df_vax70[!(df_vax70$age == 'All'),]
```

# Prevalent Vaccination Scenario

## Fig. ICER per case averted
```{r}
t <- labs(y = "$ saved per case averted", title = "Prevalent Vaccination: ICER per case averted")

ggplot(age_df_base, aes(x = age, y = icer.case.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy") + t

ggplot(df_base[(df_base$age=="All"),], aes(x = v.eff, y = icer.case.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy (%)", color = "Risk") + t

ggplot(df_base, aes(x = age, y = icer.case.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + t +
  facet_grid(~ v.eff)
```

## 40% VE: ICER per case averted
```{r}
ggplot(df_base[(df_base$v.eff == "40"),], aes(x = age, y = icer.case.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + 
  ylab("$ saved per case averted") + ggtitle("Prevalent Vaccination (40% efficacy): ICER per case averted")
```

## Fig. ICER per death averted
```{r}
t <- labs(y = "$ saved per death averted", title = "Prevalent Vaccination: ICER per death averted")

ggplot(age_df_base, aes(x = age, y = icer.death.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy") + t

ggplot(df_base[(df_base$age=="All"),], aes(x = v.eff, y = icer.death.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy (%)", color = "Risk") + t

ggplot(df_base, aes(x = age, y = icer.death.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + t +
  facet_grid(~ v.eff)
```

## 40% VE: ICER per death averted
```{r}
ggplot(df_base[(df_base$v.eff == "40"),], aes(x = age, y = icer.death.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + 
  ylab("$ saved per death averted") + ggtitle("Prevalent Vaccination (40% efficacy): ICER per death averted")
```

## Fig. ICER per DALY averted
```{r}
t <- labs(y = "$ saved per DALY averted", title = "Prevalent Vaccination: ICER per DALY averted")

ggplot(age_df_base, aes(x = age, y = icer.daly.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy") + t

ggplot(df_base[(df_base$age=="All"),], aes(x = v.eff, y = icer.daly.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy (%)", color = "Risk") + t

ggplot(df_base, aes(x = age, y = icer.daly.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + t +
  facet_grid(~ v.eff)
```

## 40% VE: ICER per DALY averted
```{r}
ggplot(df_base[(df_base$v.eff == "40"),], aes(x = age, y = icer.daly.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") + 
  ylab("$ saved per DALY averted") + ggtitle("Prevalent Vaccination (40% efficacy): ICER per DALY averted")
```

# Set up plots.
```{r}
# age
g1 <- ggplot(age_df_base, aes(x = age, group = v.eff, color = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy")
# risk
g2 <- ggplot(df_base[(df_base$age=="All"),], aes(x = v.eff, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy", color = "Risk group")

g3 <- ggplot(risk_df_base, aes(x = age, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") +
  facet_grid(~ v.eff)

g4 <- ggplot(df_base[(df_base$v.eff == "40"),], aes(x = age, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group")
```

## Fig. Cases, cases averted
```{r}
# age groups
g1 + aes(y = cases) + labs(y = "Cases", title = "Prevalent Vaccination: Cases")
g1 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "Prevalent Vaccination: Cases per 100k")
g1 + aes(y = cases.averted) + labs(y = "Cases averted", title = "Prevalent Vaccination: Cases averted")
g1 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "Prevalent Vaccination: Cases averted per 100k")

# risk groups
g2 + aes(y = cases) + labs(y = "Cases", title = "Prevalent Vaccination: Cases")
g2 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "Prevalent Vaccination: Cases per 100k")
g2 + aes(y = cases.averted) + labs(y = "Cases averted", title = "Prevalent Vaccination: Cases averted")
g2 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "Prevalent Vaccination: Cases averted per 100k")

g3 + aes(y = cases) + labs(y = "Cases", title = "Prevalent Vaccination: Cases")
g3 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "Prevalent Vaccination: Cases per 100k")
g3 + aes(y = cases.averted) + labs(y = "Cases averted", title = "Prevalent Vaccination: Cases averted")
g3 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "Prevalent Vaccination: Cases averted per 100k")
```

## 40% VE: Cases, cases averted
```{r}
g4 + aes(y = cases) + labs(y = "Cases", title = "Prevalent Vaccination (40% VE): Cases")
g4 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "Prevalent Vaccination (40% VE): Cases per 100k")
g4 + aes(y = cases.averted) + labs(y = "Cases averted", title = "Prevalent Vaccination (40% VE): Cases averted")
g4 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "Prevalent Vaccination (40% VE): Cases averted per 100k")
```

## Fig. Deaths, deaths averted
```{r}
# age groups
g1 + aes(y = deaths) + labs(y = "Deaths", title = "Prevalent Vaccination: Deaths")
g1 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "Prevalent Vaccination: Deaths per 100k")
g1 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "Prevalent Vaccination: Deaths averted")
g1 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "Prevalent Vaccination: Deaths averted per 100k")

# risk groups
g2 + aes(y = deaths) + labs(y = "Deaths", title = "Prevalent Vaccination: Deaths")
g2 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "Prevalent Vaccination: Deaths per 100k")
g2 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "Prevalent Vaccination: Deaths averted")
g2 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "Prevalent Vaccination: Deaths averted per 100k")

g3 + aes(y = deaths) + labs(y = "Deaths", title = "Prevalent Vaccination: Deaths")
g3 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "Prevalent Vaccination: Deaths per 100k")
g3 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "Prevalent Vaccination: Deaths averted")
g3 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "Prevalent Vaccination: Deaths averted per 100k")
```

## 40% VE: Deaths, deaths averted
```{r}
g4 + aes(y = deaths) + labs(y = "Deaths", title = "Prevalent Vaccination (40% VE): Deaths")
g4 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "Prevalent Vaccination (40% VE): Deaths per 100k")
g4 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "Prevalent Vaccination (40% VE): Deaths averted")
g4 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "Prevalent Vaccination (40% VE): Deaths averted per 100k")
```

## Fig. DALYs, DALYs averted
```{r}
# age groups
g1 + aes(y = dalys) + labs(y = "DALYs", title = "Prevalent Vaccination: DALYs")
g1 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "Prevalent Vaccination: DALYs per 100k")
g1 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "Prevalent Vaccination: DALYs averted")
g1 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "Prevalent Vaccination: DALYs averted per 100k")
# risk groups
g2 + aes(y = dalys) + labs(y = "DALYs", title = "Prevalent Vaccination: DALYs")
g2 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "Prevalent Vaccination: DALYs per 100k")
g2 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "Prevalent Vaccination: DALYs averted")
g2 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "Prevalent Vaccination: DALYs averted per 100k")

g3 + aes(y = dalys) + labs(y = "DALYs", title = "Prevalent Vaccination: DALYs")
g3 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "Prevalent Vaccination: DALYs per 100k")
g3 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "Prevalent Vaccination: DALYs averted")
g3 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "Prevalent Vaccination: DALYs averted per 100k")
```

## 40% VE: DALYs, DALYs averted
```{r}
g4 + aes(y = dalys) + labs(y = "DALYs", title = "Prevalent Vaccination (40% VE): DALYs")
g4 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "Prevalent Vaccination (40% VE): DALYs per 100k")
g4 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "Prevalent Vaccination (40% VE): DALYs averted")
g4 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "Prevalent Vaccination (40% VE): DALYs averted per 100k")
```

# Fig. Cost saved vs. DALYs averted
```{r}
g5 <- ggplot(df_base, aes(x = dalys.averted.per100k, y = cost.diff.per100k)) +
  labs(x = "DALYs averted per 100K", y = "Cost saved per 100K", title = "Prevalent Vaccination: Cost saved vs. DALYs averted")

g5 + aes(color = risk, group = risk) + geom_point() + facet_grid(v.eff ~ age)

g5 + aes(color = age, group = age) + geom_point() + facet_grid(v.eff ~ risk)
```

# 70% Vaccination Scenario

## Fig. ICER per case averted
```{r}
g <- ggplot(df_vax70[(df_vax70$age=="All"),], aes(x = v.eff, color = risk, group = risk))
t1 <- labs(y = "$ saved per case averted", title = "70% Vaccination: ICER per case averted")
t2 <- labs(y = "$ saved per death averted", title = "70% Vaccination: ICER per death averted")
t3 <- labs(y = "$ saved per DALY averted", title = "70% Vaccination: ICER per DALY averted")

ggplot(age_df_vax70, aes(x = age, y = icer.case.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + 
  labs(x = "Age group", color = "Vaccine \nefficacy") + t1

g + aes(y = icer.case.averted) + geom_point() + geom_line(linetype = "dotted") +
  t1 + labs(x = "Vaccine efficacy (%)", color = "Risk group")

ggplot(df_vax70, aes(x = age, y = icer.case.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(color = "Risk group") + 
  ylab("$ saved per case averted") + ggtitle("70% Vaccination: ICER per case averted") + facet_grid(~ v.eff)
```

## Fig. ICER per death averted
```{r}
ggplot(age_df_vax70, aes(x = age, y = icer.death.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + 
  labs(x = "Age group", color = "Vaccine \nefficacy") + t2

g + aes(y = icer.death.averted) + geom_point() + geom_line(linetype = "dotted") +
  t2 + labs(x = "Vaccine efficacy (%)", color = "Risk group")

ggplot(df_vax70, aes(x = age, y = icer.death.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(color = "Risk group") + 
  ylab("$ saved per death averted") + ggtitle("70% Vaccination: ICER per death averted") + facet_grid(~ v.eff)
```

## Fig. ICER per DALY averted
```{r}
ggplot(age_df_vax70, aes(x = age, y = icer.daly.averted, color = v.eff, group = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") +
  labs(x = "Age group", color = "Vaccine \nefficacy") + t3

g + aes(y = icer.daly.averted) + geom_point() + geom_line(linetype = "dotted") +
  t3 + labs(x = "Vaccine efficacy (%)", color = "Risk group")

ggplot(df_vax70, aes(x = age, y = icer.daly.averted, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(color = "Risk group") + 
  ylab("$ saved per DALY averted") + ggtitle("70% Vaccination: ICER per DALY averted") + facet_grid(~ v.eff)
```

# Set up plots.
```{r}
# age
h1 <- ggplot(age_df_vax70, aes(x = age, group = v.eff, color = v.eff)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Vaccine \nefficacy")
# risk
h2 <- ggplot(df_vax70[(df_vax70$age=="All"),], aes(x = v.eff, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Vaccine efficacy", color = "Risk group")

h3 <- ggplot(risk_df_vax70, aes(x = age, group = risk, color = risk)) +
  geom_point() + geom_line(linetype = "dotted") + labs(x = "Age group", color = "Risk group") +
  facet_grid(~ v.eff)
```

## Fig. Cases, cases averted
```{r}
# age groups
h1 + aes(y = cases) + labs(y = "Cases", title = "70% Vaccination: Cases")
h1 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "70% Vaccination: Cases per 100k")
h1 + aes(y = cases.averted) + labs(y = "Cases averted", title = "70% Vaccination: Cases averted")
h1 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "70% Vaccination: Cases averted per 100k")

# risk groups
h2 + aes(y = cases) + labs(y = "Cases", title = "70% Vaccination: Cases")
h2 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "70% Vaccination: Cases per 100k")
h2 + aes(y = cases.averted) + labs(y = "Cases averted", title = "70% Vaccination: Cases averted")
h2 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "70% Vaccination: Cases averted per 100k")

h3 + aes(y = cases) + labs(y = "Cases", title = "70% Vaccination: Cases")
h3 + aes(y = cases.per100k) + labs(y = "Cases per 100k", title = "70% Vaccination: Cases per 100k")
h3 + aes(y = cases.averted) + labs(y = "Cases averted", title = "70% Vaccination: Cases averted")
h3 + aes(y = cases.averted.per100k) + labs(y = "Cases averted per 100k", title = "70% Vaccination: Cases averted per 100k")
```

## Fig. Deaths, deaths averted
```{r}
# age groups
h1 + aes(y = deaths) + labs(y = "Deaths", title = "70% Vaccination: Deaths")
h1 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "70% Vaccination: Deaths per 100k")
h1 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "70% Vaccination: Deaths averted")
h1 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "70% Vaccination: Deaths averted per 100k")

# risk groups
h2 + aes(y = deaths) + labs(y = "Deaths", title = "70% Vaccination: Deaths")
h2 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "70% Vaccination: Deaths per 100k")
h2 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "70% Vaccination: Deaths averted")
h2 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "70% Vaccination: Deaths averted per 100k")

h3 + aes(y = deaths) + labs(y = "Deaths", title = "70% Vaccination: Deaths")
h3 + aes(y = deaths.per100k) + labs(y = "Deaths per 100k", title = "70% Vaccination: Deaths per 100k")
h3 + aes(y = deaths.averted) + labs(y = "Deaths averted", title = "70% Vaccination: Deaths averted")
h3 + aes(y = deaths.averted.per100k) + labs(y = "Deaths averted per 100k", title = "70% Vaccination: Deaths averted per 100k")
```

## Fig. DALYs, DALYs averted
```{r}
# age groups
h1 + aes(y = dalys) + labs(y = "DALYs", title = "70% Vaccination: DALYs")
h1 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "70% Vaccination: DALYs per 100k")
h1 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "70% Vaccination: DALYs averted")
h1 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "70% Vaccination: DALYs averted per 100k")
# risk groups
h2 + aes(y = dalys) + labs(y = "DALYs", title = "70% Vaccination: DALYs")
h2 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "70% Vaccination: DALYs per 100k")
h2 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "70% Vaccination: DALYs averted")
h2 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "70% Vaccination: DALYs averted per 100k")

h3 + aes(y = dalys) + labs(y = "DALYs", title = "70% Vaccination: DALYs")
h3 + aes(y = dalys.per100k) + labs(y = "DALYs per 100k", title = "70% Vaccination: DALYs per 100k")
h3 + aes(y = dalys.averted) + labs(y = "DALYs averted", title = "70% Vaccination: DALYs averted")
h3 + aes(y = dalys.averted.per100k) + labs(y = "DALYs averted per 100k", title = "70% Vaccination: DALYs averted per 100k")
```

# Fig. Cost saved vs. DALYs averted
```{r}
h5 <- ggplot(df_vax70, aes(x = dalys.averted.per100k, y = cost.diff.per100k)) +
  labs(x = "DALYs averted per 100K", y = "Cost saved per 100K", title = "70% Vaccination: Cost saved vs. DALYs averted")

h5 + aes(color = risk, group = risk) + geom_point() + facet_grid(v.eff ~ age)

h5 + aes(color = age, group = age) + geom_point() + facet_grid(v.eff ~ risk)
```
